---
title: "Week 4 Part 1"
author: "Carly Norris"
date: "11/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Confidence intervals associated with a sample

Using t distribution because it accounts for greater uncertainty and our pop SD is unknown. Running a t-test on the single sample created.
The 95% confidence interval we would expect to find the mean 95% percent of the time within this interval. 

Report: Mean, n=x, SD and 95% confidence interval of the sample for general reporting of the central tendancy associated with the sample. 

```{r}
otter_length <- c(38, 41,50,27,32,41,48,60,43)

t.test(otter_length)
```
## T-test (1-sample t-test)

Run ?t.test in the console to see arguments and edit the settings of the T-test

mu= is the null hypothesis to test in this case mean otter length =50in

See a claim: mean otter length is 50 inches

```{r}
otter_test <- t.test(x= otter_length, mu=50)
otter_test
```
If the pop mean is 50in then there is a 4.44% chance that we could have randomly taken a sample from the pop that has a mean that as least as different from 50 as our sample mean is in either direction. 

When we do a two sample t-test. Are the differences between my two sample means are soo different that it more likely that they are drawn from different populations. 

## Two-sample t-test

```{r}
desert_bighorns <- c(32, 44, 18, 26, 50, 33, 42, 20)
sierra_bighorns <- c(28, 31, 40, 42, 26, 29, 31)

t.test(x= desert_bighorns, y= sierra_bighorns)
```
The 95% confidence interval in a two-sample t-test is the difference between the two sample means. It can be negaitve because it can be y-x or x-y. We would expect the difference between the two sample means to be within this range 95% of the time. NOt as significant. 

df= represents sample size
t= 
p-value= prob these samples are drawn from a pop with the same mean

If the p-value prob is high there is a good chance that the samples are drawn from pops with the same mean. If the p-value is super low then there is a good chance the samples were drawn from dif pops. 









